---
title: "BBN Sentiments Analysis"
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    horizontal_layout: scroll
runtime: shiny
---


```{r}
library(dplyr)
library(readr)
library(tidyr)
library(ggplot2)
library(scales)
library(knitr)
library(shiny)
library(shinydashboard)
library(tidytext)
library(flexdashboard)
library(wordcloud2)

tweets<- read_csv("bbn_tweets.csv") %>% mutate(Housemate = ifelse(is.na(Housemate), 'Unassigned', Housemate))

options(scipen = 100, digits = 4)
#tweets <- rename(tweets, Sentiments = sentiment)

```





Dashboard Overview {data-icon="fa-bar-chart"}
=====================================


Sidebar {.sidebar}
--------------------------------------
```{r}
selectInput('housemate', "Housemate", c('All',unique(tweets$Housemate)))

renderText('Choose an Housemate, to view their info on all pages')
```


## row {data-height=150}

### Number of Negative tweets
```{r}
Tweets <- reactive({
  if(input$housemate == 'All'){
    tweets
  } else {
  tweets %>% filter(Housemate == input$housemate)}
  })

number_by_sentiments <- reactive({Tweets() %>%
  group_by(sentiment) %>%
  summarise(Number = n())
  })


renderValueBox({valueBox(format(number_by_sentiments()[[1, 2]], big.mark=','),
                         icon = 'fa-face-smile-beam', color = "firebrick")})
```

### Number of Positive tweets
```{r}

renderValueBox({valueBox(format(number_by_sentiments()[[2, 2]], big.mark = ','), 
                         icon = "fa-twitter",
                         color = "forestgreen")})
```

### Total Number Of tweets
```{r}
renderValueBox({valueBox(format(nrow(Tweets()), big.mark = ','), icon = "fa-twitter-square", color = "darkorchid")})
```

### Number of Users
```{r}
user_count_mention <- reactive({n_distinct(Tweets()$Username)})

renderValueBox({valueBox(format(user_count_mention(), big.mark=','), icon = "fa-users", color = "darkorchid")})
```

### Total Number Of Engagements
```{r}
engage <- reactive({
            Tweets() %>%
            summarise(retweets = sum(retweet_count, na.rm = TRUE), 
            favourites = sum(favorite_count, na.rm = TRUE))
  
})
  


renderValueBox({
  valueBox(format(nrow(Tweets()) + engage()$retweets + engage()$favourites, big.mark = ','), 
                icon = "fa-twitter", color = "warning")
  })
```


tabpanel {.tabset .tabset-fade}
---------------------------------------------------------------

### Sentiment Overview

```{r echo=FALSE, message=FALSE, warning=FALSE}
renderPlot({Tweets() %>% 
  group_by(sentiment) %>%
  summarise(count = n()) %>%
  mutate(percentage = count/sum(count) * 100) %>%
  ggplot(aes(sentiment,percentage, fill=sentiment)) +
  geom_bar(stat="identity") +
  geom_text(aes(label = paste(round(percentage,2), "%", sep="")), nudge_y = 4, size=3) +
  theme_minimal()})
```

### WordCloud

```{r echo=FALSE}

customstops <- reactive({
  data.frame(word = c("null", "rt", "retweet", "follow", "dm", "don",
                      "ve", "lol", "ll", "ii",    "konga", 'bbnaija', 
                      'bbnaijas', "bellaokugbe",'na', 'didn', 'dey', 
                      'groovymono', 'groovers', 'groophy', 'fans', 'chi', 
                      'beautytukara', 'tukara','bellaokagbue','hermesx',
                      'bbnaijas', 'girl', 'house', 'vote', 
                      tolower(input$housemate)))
  })

words <-  reactive({ 
            Tweets() %>%
                   select(tweets) %>%
                   unnest_tokens(word, tweets) %>%
                   anti_join(stop_words, by = c("word" = "word")) %>%
                   anti_join(customstops(), by = c("word" = "word")) %>% 
                   count(word, sort=TRUE) %>% 
                   filter(!is.na(word))
  })

                   



renderWordcloud2(wordcloud2(data=head(words(), 50),
                            size=1, 
                            color='random-dark', 
                            shape = 'pentagon'))
```

### Negative WordCloud

```{r echo=FALSE}
neg_words <-  reactive({Tweets() %>%
                     filter(sentiment == 'Negative') %>%
                     select(tweets) %>%
                     unnest_tokens(word, tweets) %>%
                     anti_join(stop_words, by = c("word" = "word")) %>%
                     anti_join(customstops(), by = c("word" = "word")) %>%
                     count(word, sort=TRUE) %>% 
                     filter(!is.na(word))})

                   




renderWordcloud2(wordcloud2(data=head(neg_words(), 50),
                            size=1.2,
                            color='random-dark', 
                            shape = 'pentagon'))
```

### Positive WordCloud

```{r echo=FALSE}

pos_words <-  reactive({Tweets() %>%
                     filter(sentiment == 'Positive') %>%
                     select(tweets) %>%
                     unnest_tokens(word, tweets) %>%
                     anti_join(stop_words, by = c("word" = "word")) %>%
                     anti_join(customstops(), by = c("word" = "word")) %>%
                     count(word, sort=TRUE) %>% 
                     filter(!is.na(word))})



renderWordcloud2(
  wordcloud2(data=head(pos_words(), 50),
                  size=1.5, 
                  color='random-dark', 
                  shape='pentagon')
)
```



Word Analytics {data-icon="fa-comments"}
=====================================

## Row

### Unique Words
```{r}
renderValueBox({valueBox(nrow(words()), icon = "fa-user", color = "darkorchid")})
```


### Unique tweets
```{r}
renderValueBox({valueBox(nrow(Tweets()), icon = "fa-close", color = "darkorchid")})
```


tabpanel {.tabset .tabset-fade}
---------------------------------------------------------------

### Popular Terms
```{r echo=FALSE, message=FALSE, warning=FALSE}
# Create a bar plot using terms with more than 60 counts
renderPlot({ggplot(head(words(),20), aes(x = reorder(word, n), y = n)) + 
  geom_bar(stat = "identity", fill = "purple") + 
  theme(axis.text.x = element_text(angle = 30, hjust = 1)) + 
  ggtitle("Popular Terms") +
  coord_flip() +
  xlab("Words") +
  ylab("Count") +
  theme_bw()})
```


### Top Negative Words
```{r echo=FALSE, message=FALSE, warning=FALSE}

renderPlot({ggplot(head(neg_words(),20), aes(x = reorder(word, n), y = n)) + 
  geom_bar(stat = "identity", fill = "firebrick", col = 'grey0') + 
  theme(axis.text.x = element_text(angle = 30, hjust = 1)) + 
  ggtitle("Popular Terms") +
  coord_flip() +
  xlab("Words") +
  ylab("Count") +
  theme_bw()})
```


### Top Positive Words
```{r echo=FALSE, message=FALSE, warning=FALSE}
# Create a bar plot using terms with more than 60 counts

renderPlot({ggplot(head(pos_words(),20), aes(x = reorder(word, n), y = n)) + 
  geom_bar(stat = "identity", fill = "forestgreen", col = 'grey0') + 
  theme(axis.text.x = element_text(angle = 30, hjust = 1)) + 
  ggtitle("Popular Terms") +
  coord_flip() +
  xlab("Words") +
  ylab("Count") +
  theme_bw()})
```


Engagement Analytics {data-icon="fa-retweet"}
=====================================


## row {data-height=150}


### Number Of Retweets
```{r}

renderValueBox({valueBox(format(engage()$retweets, big.mark = ','),
                         icon = "fa-envelope", 
                         color = "skyblue")})
```


### Number Of Likes
```{r}
renderValueBox({valueBox(format(engage()$favourites, big.mark = ','), 
                         icon = 'fa-heart', 
                         color = "goldenrod")})
```


### Total Number Of Engagements
```{r}
renderValueBox({
  valueBox(format(nrow(Tweets()) + engage()$retweets + engage()$favourites, big.mark = ','), 
                icon = "fa-twitter", color = "info")
  })
```



tabpanel {.tabset .tabset-fade}
---------------------------------------------------------------

### Retweet Total Engagement By Housemate
```{r}
engagements <- tweets %>%
   filter(Housemate != 'Unassigned') %>%
   group_by(Housemate) %>% 
   summarise(tweet_count = n(), 
             retweet_count = sum(retweet_count, na.rm = TRUE), 
             favorite_count = sum(favorite_count, na.rm = TRUE),
             engagement_count =  tweet_count + retweet_count + favorite_count)


engagements %>% 
  ggplot(aes(x = reorder(Housemate, engagement_count), y = engagement_count)) +
  geom_bar(stat = "identity", fill = "darkolivegreen4", col =  'gray0') + 
  theme(axis.text.x = element_text(angle = 30, hjust = 1)) + 
  ggtitle("Popular Terms") +
  coord_flip() +
  xlab("Words") +
  ylab("Count") +
  theme_bw()
```


### Retweets By Housemates
```{r}
engagements %>% 
  ggplot(aes(x = reorder(Housemate, retweet_count), y = retweet_count)) +
  geom_bar(stat = "identity", fill = "darkslategray3", col =  'gray0') + 
  theme(axis.text.x = element_text(angle = 30, hjust = 1)) + 
  ggtitle("Popular Terms") +
  coord_flip() +
  xlab("Words") +
  ylab("Count") +
  theme_bw()
```


### Likes By Housemates
```{r}
engagements %>% 
  ggplot(aes(x = reorder(Housemate, favorite_count), y = favorite_count)) +
  geom_bar(stat = "identity", fill = "goldenrod", col =  'gray0') + 
  theme(axis.text.x = element_text(angle = 30, hjust = 1)) + 
  ggtitle("Popular Terms") +
  coord_flip() +
  xlab("Words") +
  ylab("Count") +
  theme_bw()
```



View Tweets {data-icon="fa-twitter"}
=====================================


tabpanel {.tabset .tabset-fade}
---------------------------------------------------------------

### Positive Tweets
```{r}
renderDataTable({Tweets() %>%
filter(sentiment == 'Positive') %>%
select(Text, retweet_count, favorite_count)},
options = list(
scrollY = '300px', paging = FALSE)
)
```


### Negative Tweets
```{r}
renderDataTable({Tweets() %>%
filter(sentiment == 'Negative') %>%
select(Text, retweet_count, favorite_count)},
options = list(
scrollY = '300px', paging = FALSE))
```


### Neutral Tweets
```{r}
renderDataTable({Tweets() %>%
filter(sentiment == 'Neutral') %>%
select(Text, retweet_count, favorite_count)},
options = list(
scrollY = '300px', paging = FALSE))
```






